The watershed transform in ITK - discussion and new developments

### 2006-05-15 article/Article.tex
added the artificial plateau image with colour.
darcs-hash:20060515070152-fafb9-3be25a780d6b4ede47f6d06a0a0fe32db592334c.gz

Another major advance made soon after by Meyer and Beucher
\cite{Beucher93a,Meyer1994a}. Meyer defined the watershed transform in terms of {\em
topographic distances} through {\em lower complete} images. These
definitions rigorously defined the behavior in the presence of
plateaus and lead to some new algorithms based on graph theory. Two
examples of these algorithms are {\em hill-climbing} and {\em image
integration} and will be discussed in more detail in this report.
Figure \ref{fig:cthead1-markers} and \ref{fig:difficult-cases} illustrate
the possible problem with plateaus.

@@

>>>>

Another major advance made soon after by Meyer and Beucher
\cite{Beucher93a,Meyer1994a}. Meyer defined the watershed transform in terms of {\em
topographic distances} through {\em lower complete} images. These
definitions rigorously defined the behavior in the presence of
plateaus and lead to some new algorithms based on graph theory. Two
examples of these algorithms are {\em hill-climbing} and {\em image
integration} and will be discussed in more detail in this report.
Figures \ref{fig:cthead1-markers}, \ref{fig:circle}and \ref{fig:difficult-cases} illustrate
the possible problems with plateaus.

@@

\begin{figure}[htbp]
\begin{center}
\subfigure[Input image - bright ring on constant background]{\includegraphics[scale=0.7]{circle_plateau}}
% \subfigure[]{\includegraphics[scale=0.7]{cthead1mf-rgb}}
% \subfigure[]{\includegraphics[scale=0.7]{cthead1mF-rgb}}
% \subfigure[]{\includegraphics[scale=0.7]{cthead1Mf-rgb}}
\subfigure[Morphological watershed]{\includegraphics[scale=0.7]{circle_rgb2}}
\subfigure[ITK watershed]{\includegraphics[scale=0.7]{circle_rgb1}}
\caption{Another example of plateau problem. The inside and outside of the ring have the same brightness, but the ring is arbitarily assigned to the outer region by the ITK watershed. It is split by the morphological watershed.\label{fig:circle}}
\end{center}
\end{figure}
